Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-26 draft.tex

\section*{Introduction}
There is a replication crisis in Science. This crisis has been
highlighted in fields as diverse as medicine \citep{ioannidis:2005},
psychology \citep{nosek:2015}, the political sciences \citep{janz:2015},
and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
behind such non-reproducibility are as diverse as the domains in which it occurs.
In medicine, factors such as {\em study power and bias, the
number of other studies on the same question, and importantly, the
ratio of true to no relationships among the all relationships probed}
have been highlighted as important causes \citep{ioannidis:2005}. 
In psychology, non-reproducibility has been blamed on spurious p-values (p-hacking),
while in the biomedical sciences, \citep{iqbal:2016}
a {\em lack of access to full datasets and detailed protocols for both
clinical and non-clinical biomedical investigation} is seen as a
critical factor. Surprisingly, the computational sciences (in the broad
sense) and computer sciences (in the strict sense) are no exception
despite the fact they rely heavily on code and data, which should
make them immune to the aforementioned problems.\\

>>>>

\section*{Introduction}
There is a replication crisis in Science. This crisis has been
highlighted in fields as diverse as medicine \citep{ioannidis:2005},
psychology \citep{nosek:2015}, the political sciences \citep{janz:2015},
and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
behind such non-reproducibility are as diverse as the domains in which it occurs.
In medicine, factors such as {\em study power and bias, the
number of other studies on the same question, and importantly, the
ratio of true to no relationships among the all relationships probed}
have been highlighted as important causes \citep{ioannidis:2005}. 
In psychology, non-reproducibility has been blamed on spurious p-values (p-hacking),
while in the biomedical sciences, \citep{iqbal:2016}
a {\em lack of access to full datasets and detailed protocols for both
clinical and non-clinical biomedical investigation} is seen as a
critical factor.
The same remarks were recently issued for chemistry \citep{coudert:2017}.
Surprisingly, the computational sciences (in the broad
sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009}
despite the fact they rely heavily on code and data, which should
make them immune to the aforementioned problems.\\
